Community context determines competition vs. facilitation trade-offs in pollination systems

### 2019-11-24 paper/manuscript.Rmd
Improve front page

**Number of words:** `r abs_wordcount$n_words_stri` in abstract; `r format(round(msc_wordcount$n_words_stri), big.mark = ",")` in main text (including Methods section).

<!-- **Number of displays:** `r n_displays$figures` figures; `r n_displays$tables` tables; `r n_displays$text_boxes` text boxes. -->

<!-- **Number of references:** `r n_references` -->

@@

<!-- **Data accessibility:** All data and code necessary to reproduce the results has been included in the Electronic Supplementary Materials and will be publicly available in appropriate databases upon acceptance.. -->

<!-- **Author contributions:** EFC wrote the manuscript and performed all analyses with input from all authors; HJM collected the data; all authors contributed to the study design.  -->

<!-- **Competing interests:** The authors have declared that no competing interests exist. -->

>>>>

**Number of words:** `r abs_wordcount$n_words_stri` in abstract; `r format(round(msc_wordcount$n_words_stri), big.mark = ",")` in main text.

**Number of displays:** `r n_displays$figures` figures; `r n_displays$tables` tables; `r n_displays$text_boxes` text boxes.

**Number of references:** `r n_references`

@@

**Data accessibility:** All data and code necessary to reproduce the results has been included in the Electronic Supplementary Materials and will be publicly available in appropriate databases upon acceptance.

**Author contributions:** EFC wrote the manuscript and performed all analyses with input from all authors; HJM collected the data; all authors contributed to the study design.

**Competing interests:** The authors have declared that no competing interests exist.
